\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\textbf{Lesson Plan Week 1 INFM 600 August 31 \& September 1}

• Administrivia Review of syllabus and course policies

• Topics Course introduction; Git \& and command line basics; Git for
collaboration; intellectual

property

• Assignment Pre-course survey due at start of class

• Readings Git install \& tutorial; command line basics

• Guest Lecture Jonathan Brier

6:00 -- 6:05 Welcome \& overview (5 min)

Give breakdown of how the class will go.

6:05 -- 6:25 Icebreaker and attendance -- a little about you slide from
survey (bad visualization then good of the data for data presentation)

Other policies slides

6:25 -- 6:35 Andrea Intro Video

This is an experimental course and please speak up if you are confused
or something is not clear.

Me:

Why are we doing this via command line?

-open a file and not all programs can handle programs

-difference between systems and platforms (we will use an emulator for
the

(emulator exercise -- 15 minutes)

(if reporting out add 15 minutes)

Show of hands on who installed the software (build in 5-10 min to
install as needed)

Explanation:

Why are we using version control?

Why git?

- collaboration

- reproducibility

- integration of change and procedural history

Course repository creation on github as a group activity. Possibly
ecoforecasting push and pull exchange

Github Guide or other hands on activity (30-45 minutes)

push and pull activity

Examples of non code use of github and how version control is expanding
from code.

Lead into conversation of licenses

- ask if people know what licenses mean

-creative commons, mit and other github listed creative commons

terms of use vs licensing

-data reuse is still a relatively new area and there

follow up the conversation in 10-15 work in pairs to look for license
for terms of use and licenses report back what did they find. (not front
page licenses where people) this is a preview on the topics for next
week, but this applies more broadly. (8 minutes search, rest is
discussion)

find 6 data where I've verified the information to hand out on paper
slips to groups to look for the data

Note the github desktop client does not sync right away and we will be
using the timestamp of the submit as the final assignments. Prepare.

Reminder for next week:

-Survey

-Finding data info seeking -- due in two weeks ( read up on it and bring
any questions for next week as you will have one week and the search
will take more time than you think) Discussion will

-reading

How the assignments fit together and the flow of the class are critical
on the syllabus. Note: How Andrea has high expectations and you're
likely to get a lower grade on the first assignment.

Reiterate we're experimenting and very accommodating to adapting to the
challenges discovered in the class.

6:25 -- 6:45 Content

6:45 -- 7:00 Content

7:00 -- 7:10 BREAK

Introduction to myself -- who and I

7:10 -- 7:45 Activity

7:45 -- 8:00 Content

8:00 -- 8:45 Etc.

Screenshot for slide: https://twitter.com/ReadTheSyllabus

Screenshots of git used by corporations.

Why is IP is important. Country by country differences to IP. Aslk for
identifying differences.

Post slides Friday Morning

\end{document}
