\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

INFM 600 Week 4 Iceberg Model Analysis Scenario

You're Andrew, a new grad student in the MIM program, and you just ran
into Barbara, one of your INFM 600 team members, right before class. You
\& Barbara started talking over a recent issue: your first team project
deliverable was due this week and Charlie, the third member of your
group, didn't do anything to contribute. You and Barbara worked together
via Google Docs and Chat for half the day on Saturday to get everything
ready and submitted.

Charlie had promised to send her notes before the meeting and had agreed
to the meeting time, but you never got the notes and she wasn't online
for your team meeting. In fact, Charlie didn't answer any of your emails
about the assignment and meeting. You sent 3 emails with reminders and
follow-up in the week prior to the due date, and Barbara had sent 2 as
well.

As you sit down for class, you notice Charlie isn't in the room yet. You
and Barbara gossip a little -- you've only known Charlie for a couple of
weeks and she was cool when you first met, but seemed distracted last
week in class and couldn't answer any of the questions when the
instructor called on her. What was up with that?

At the break, Charlie still hasn't made it, so you and Barbara start
planning your next steps: an intervention is needed; you can't have your
team project falling apart before it's even started! You and Barbara
agree that a careful approach is needed to avoid making things worse, so
you decide to use a handy ``systems thinking'' analysis tool you learned
about in class to consider some of the reasons behind Charlie's no-show
behavior before deciding how to move forward.

\end{document}
