\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\textbf{Lesson Plan Week 6 INFM 600 October 5 \& 6}

6:00 -- 6:05 Welcome \& overview (5 min)

6:05 -- 6:25 Ethics: definitions, framing. Discuss: why paired with data
cleaning?

6:25 -- 6:45 Vitak et al key points: Belmont principles, ethics issues
in social media data. Discuss how ethics attitudes can impact data
cleaning \& other parts of information life cycle.

6:45 -- 7:00 Van den Broeck et al key points: process of screening,
diagnosing, treating data; examples from online discussion

7:00 -- 7:10 BREAK

7:10 -- 7:55 Demo: walk-through data cleaning in Excel.

7:55 -- 8:40 Activity: working with project group, pick 1-2 columns of
data and test data cleaning procedures. ANNOUNCE: PREP IN ADVANCE -- IF
BIG DATA SET, EXTRACT \textasciitilde{}500 ROWS.

8:40 -- 8:45 Reminder -- Need Wikimedia/Wikipedia account next week

Demo details:

Give headers: what are assumptions? List prior expectations.

Discuss what steps are needed for whole data set, what is needed for
specific types of attributes.

Check prior expectations, making notes on process \& results in txt
file.

Example tasks:

\begin{itemize}
\item
  transform Likert to numerals \& generate distributions.
\item
  Check distributions of values, find outliers \& examine details.
\item
  Fill null fields: what rationales?
\item
  Identify records to drop and why
\item
  Check for character set issues
\item
  Check temporal ordering for ``impossible'' sequences
\item
  Verify there are no ``illegal'' values
\item
  Distributions -- min, max, mean, sd (for identifying outliers)
\end{itemize}

\end{document}
