\documentclass[12pt]{article}
\usepackage[letterpaper, left=0.5in, right=0.5in, top=1in, bottom=1in]{geometry}
\usepackage[thinlines]{easytable}
\newcommand\tab[1][0.25cm]{\hspace*{#1}}
\usepackage{titling}
\usepackage{tabulary}

\title{INFM 600 Team Presentation}
%\author{Due Week #}
\date{\vspace{-10ex}}%removes date from maketitle display

\begin{document}
	\maketitle
		\renewcommand{\arraystretch}{2}
		\begin{tabulary}{6.5in}{| p{2.75in} | p{2.5in} | c | c |}
			\hline
			\textbf{Component} & \textbf{Comments} & \textbf{Worth} & \textbf{Given}\\
			\hline
			Did the team cover sufficient breadth and depth of information in the presentation?  & &  1/10 & \\
			\hline
			Was the presentation within the time limit? & & 1/10 &\\
			\hline
			Was the target audience for the analysis made clear in the presentation, and was the presentation designed to communicate effectively to that audience? & & 2/10 & \\
			\hline
			Were the specific questions and their relevance to the target audience made clear in the presentation? & & 1/10 & \\
			\hline
			Were the results of analyses presented in a way that supports a decision by the target audience? & & 1/10 & \\
			\hline
			Did the presentation use graphics and images effectively? & &  1/10 & \\
			\hline
			Was everyone on the team able to respond to questions about the presentation? & & 1/10 & \\
			\hline
			Was the presentation professionally delivered, with smooth transitions between presenters (if applicable)? & &  1/10 & \\
			\hline
			Did the team project a professional appearance and level of preparedness? & & 1/10 & \\
			\hline
		\end{tabulary}

\begin{flushright}
	\textbf{Total:}\tab[3.3cm]
\end{flushright}


	\textbf{General Comments:}

	
\end{document}